### 2017-04-04 paper/oopsla17-submission/evaluation-accuracy.tex
update some eval numbers, more to come

\paragraph{Results}
\autoref{fig:accuracy-results} shows the results of our experiment.
%
Localizing the type errors in our benchmarks amounted, on average, to
selecting one of 2--3 correct locations out of a slice of 10--11.
%
Our baseline of selecting at random achieves 30\% Top-1
accuracy (58\% Top-3), while \ocaml achieves a Top-1 accuracy of 45\%.
%
Interestingly, one only needs two \emph{random} guesses to outperform
\ocaml, with 47\% accuracy.
%
\sherrloc outperforms both baselines with 56\% Top-1 accuracy (84\% Top
3), while \mycroft actually underperforms \ocaml with 38--41\% Top-1
accuracy.
%
Finally, we find that \emph{all} of our classifiers outperform \sherrloc,
ranging from 60--62\% Top-1 accuracy (85--88\% Top-3) for the \linear
classifier to 71--73\% Top-1 accuracy (91\% Top-3) for the \hiddenFH.

Surprisingly, there is little variation in accuracy between classifiers.
With the exception of the \linear model, they all achieve around 70\%
Top-1 accuracy and around 90\% Top-3 accuracy.
%
This suggests that the model they learn is relatively
simple.
%
In particular, notice that although the \hiddenT has $50\times$ \emph{fewer}
hidden neurons than the \hiddenFH, it only loses around 2\% accuracy.
% In particular, notice that the \hiddenT only loses around 2\% accuracy
% compared to the \hiddenFH,
%
We also note that our classifiers consistently perform better when
trained on the \FALL programs and tested on the \SPRING programs than
vice versa, they appear to generalize better from the \FALL data. 
FIXME: Why? What is your explanation for this? Is it just sizes of those 
datasets or something qualitative about the program pairs in them?

>>>>

\paragraph{Results}
\autoref{fig:accuracy-results} shows the results of our experiment.
%
Localizing the type errors in our benchmarks amounted, on average, to
selecting one of 3 correct locations out of a slice of 10.
%
Our baseline of selecting at random achieves 30\% Top-1
accuracy (58\% Top-3), while \ocaml achieves a Top-1 accuracy of 45\%.
%
Interestingly, one only needs two \emph{random} guesses to outperform
\ocaml, with 47\% accuracy.
%
\sherrloc outperforms both baselines with 56\% Top-1 accuracy (84\% Top
3), while \mycroft actually underperforms \ocaml with 38--41\% Top-1
accuracy.
%
Finally, we find that \emph{all} of our classifiers outperform \sherrloc,
ranging from 59--63\% Top-1 accuracy (86--88\% Top-3) for the \linear
classifier to 70--74\% Top-1 accuracy (91--92\% Top-3) for the \hiddenFH.

Surprisingly, there is little variation in accuracy between classifiers.
With the exception of the \linear model, they all achieve around 70\%
Top-1 accuracy and around 90\% Top-3 accuracy.
%
This suggests that the model they learn is relatively simple.
%
In particular, notice that although the \hiddenT has $50\times$ \emph{fewer}
hidden neurons than the \hiddenFH, it only loses around 2\% accuracy.
% In particular, notice that the \hiddenT only loses around 2\% accuracy
% compared to the \hiddenFH,
%
We also note that our classifiers consistently perform better when
trained on the \FALL programs and tested on the \SPRING programs than
vice versa.
% , they appear to generalize better from the \FALL data.
% FIXME: Why? What is your explanation for this? Is it just sizes of those
% datasets or something qualitative about the program pairs in them?
